Self Regulation Ontology Retest Analyses

### 2018-05-02 code/SRO_Retest_Analyses.Rmd
fyp slides

demog_rel_df %>%
  mutate(var = row.names(.)) %>%
  select(var, icc, spearman, pearson) %>%
  arrange(-icc)
```

@@

Post process dv's from cluster to calculate reliabilities
```{r}
t1_dvs = read.csv(paste0(retest_data_path, 't1_tbt_dvs.csv'))
t2_dvs = read.csv(paste0(retest_data_path, 't2_tbt_dvs.csv'))
```

>>>>

demog_rel_df = demog_rel_df %>%
  mutate(var = row.names(.)) %>%
  select(var, icc, spearman, pearson) %>%
  arrange(-icc)

demog_rel_df
```

```{r}
sjt.df(demog_rel_df %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/demog_rel_table.doc")
```

@@

Post process dv's from cluster to calculate reliabilities
```{r}
t1_dvs = read.csv(paste0(retest_data_path, 't1_tbt_dvs.csv'))
t1_dvs = t1_dvs %>% select(-X) 
t2_dvs = read.csv(paste0(retest_data_path, 't2_tbt_dvs.csv'))
t2_dvs = t2_dvs %>% select(-X)

t1_dvs = t1_dvs %>% mutate(sub_id = as.character(sub_id))
t2_dvs = t2_dvs %>% mutate(sub_id = as.character(sub_id))

unique(t2_dvs$sub_id)

t1_dvs[,c("acc","sub_id", "breaks")] %>%
  left_join(t2_dvs[,c("acc","sub_id", "breaks")], by = c("sub_id", "breaks")) %>%
  distinct()
```
